---
title: "SurvivalAnalysis_NormalizedDrugs_GEO"
author: "Yusuke Suita"
date: "2022-11-10"
output: html_document
runtime: shiny
---

The goal of this study is to determine optimal drugs for a specific subtype. 
To achieve the goal, this script returns survival analysis on the selected patient groups (group with a particurally subtype and two different treatment groups). Using this survival analysis, you can test the effect of a drug on a particular subtype of patients.

Inputs are GEO correctal cancer patients (sample_id) with overall survival data (e.g. overall survival, progression_free_survival), subtype, and treatments

Expected outputs are survival analysis for population of the patients with specific subtypes and treatments

## Download libraries
```{r setup, include=FALSE}
library(dplyr)
library(survminer)
library(survival)
library(tidyr) 
library(shiny)
```

## Data inputs and data cleaning
```{r eruptions, echo=FALSE}
#Install treatment and clinical data
##Treatment/survival data with normalized drugs
col_norm_treat<-read.csv(file="/Users/ysuita/Desktop/Disease_Subtyping_2022/GSE72970_sample_metadata_raw.csv")
#Create table for list of drugs
table(col_norm_treat$normalized_drug)

#col_norm_treat_clean<-col_norm_treat[c("sample_id","normalized_drug","progression_free_survival","overall_survival")]

##Subtype data
subtype<-read.csv(file="/Users/ysuita/Desktop/Disease_Subtyping_2022/gse72970_cmscaller_subtype.csv")
colnames(subtype)[1:2]<-c("sample_id","subtype")
colnames(subtype)

##Combine treatment/survival/subtype data based on sample_id
combined<-merge(col_norm_treat_clean,subtype,by="sample_id")
#remove NA rows
combined_clean<-combined %>% drop_na
#add vital status
combined_clean$vital_status<-rep(c(1),rep=nrow(combined_clean))
```

##Drug/subtype selection and survival analysis function 
```{r}
compared_drugs<-function(drug1,drug2,subtype){
###Pick 2 treatments
combined_clean_druginterest<-combined_clean[combined_clean$normalized_drug==drug1|combined_clean$normalized_drug==drug2,]

###Pick subtype
combined_clean_druginterest_subtypeinterest<-combined_clean_druginterest[combined_clean_druginterest$subtype==subtype,]

###Survival analysis
fit <- surv_fit(Surv(time = overall_survival,event = vital_status ) ~ normalized_drug ,data=combined_clean_druginterest_subtypeinterest)
ggsurvplot(fit, data = combined_clean_druginterest_subtypeinterest, risk.table = TRUE, conf.int = TRUE,pval=TRUE)
}
```

##Run function 

Usage of this function: Put drug names listed in the drug table above (ex. drug1="fluorouracil|leucovorin|irinotecan" drug2="bevacizumab|fluorouracil|leucovorin|irinotecan") and pick subtype from CMS1, CMS2, CMS3, or CMS4. 
```{r}
#Input examples
compared_drugs(drug1="fluorouracil|leucovorin|irinotecan", drug2="bevacizumab|fluorouracil|leucovorin|irinotecan", subtype="CMS3")
```
